%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
\usepackage{cmbright}
% \usepackage{fontenc}
% \usepackage{times}
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
{\fontfamily{cmbr}\selectfont\textbf{\Huge\scshape Mekaeel Malik}}
\\ \vspace{3pt}
    \small 647-712-4597 $|$ \href{mailto:mekaeel.r.malik@gmail.com}{\underline{mekaeel.r.malik@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/mekaeel-m/}{\underline{linkedin.com/in/mekaeel-m}} $|$
    \href{https://github.com/mekaeel-m}{\underline{github.com/mekaeel-m}}
\end{center}
\vspace*{-15pt}  % Adjust as needed

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {McMaster University}{Hamilton, ON}
      {Pursuing a Bachelor of Computer Science, Minor in Innovation. MES Council Representative}{Sept. 2024 -- present}
      \resumeItemListStart
        \resumeItem{Key Courses: Software Development, Data Structures \& Algorithms, Web Development, Logical Reasoning}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Software Engineer Intern/Coop} {May 2025 -- August 2025}
      {TD Bank Canada}{Hybrid / Toronto, ON}
      \resumeItemListStart
        \resumeItem{Delivered a scalable solution for on-demand event processing, addressing high-volume authentication needs (\textbf{100,000+ monthly requests}) by developing and deploying \textbf{RESTful API} using Spring Framework.}
        \resumeItem{Realized a \textbf{50\% reduction in API load time} by identifying API bottlenecks and implementing \textbf{pre-caching} for overlapping data using Spring Data.}
        \resumeItem{Collaborated with senior team members to reduce data overload through \textbf{database normalization} cutting \textbf{database size by 10\%+} and reducing \textbf{API response size by 5\%}.}
        \resumeItem{Assisted with development of API adapter to r\textbf{educe unnecessary sub-calls by 60\%} through consolidation.}
        \resumeItemListEnd

    \resumeSubheading
      {Undergraduate Research Assistant} {August 2025 -- Present}
      {McMaster University}{Hamilton, ON}
      \resumeItemListStart
        \resumeItem{Collaborated with faculty and research team to design machine learning models \textbf{predicting NBA player injury risk}, generating \textbf{actionable insights} for performance and risk management.}
        \resumeItem{Collected datasets from web and API sources using \textbf{Selenium} and Beautiful Soup. Cleaned and \textbf{merged datasets using SQL} to build analysis-ready tables.}
        \resumeItem{Trained and evaluated Scikit-learn models on \textbf{10,000+ NBA game logs and injury reports} using Python to identify player health and injury trends.}
        \resumeItem{Contributed to \textbf{forthcoming research publication} by documenting methodology, experimental results, and recommendations for broader applications of predictive analytics.}
        \resumeItemListEnd

    \resumeSubheading
      {Software Developer - Summer Intern} {July 2024 -- August 2024}
      {Infinite Investment Systems}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Created \textbf{browser-based testing of internal sites} using Selenium increasing test coverage by 30\%.}
        \resumeItem{Wrote integration tests for API endpoints utilizing \textbf{Requests library} to decreasing runtime by 10ms.}
        \resumeItem{Met internal testing needs by creating testing data using Faker and Pandas to \textbf{generate 50+ GBs of data.}}
    \resumeItemListEnd
    
      
% -----------Multiple Positions Heading-----------
   % \resumeSubSubheading
   %  {Software Engineer I}{Oct 2014 - Sep 2016}
   %  \resumeItemListStart
   %     \resumeItem{Apache Beam}
   %       {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
   %  \resumeItemListEnd
   % \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Database Administrator}{June 2022 -- Sept. 2022}
      {Penny Appeal Canada}{Mississauga, ON}
        \resumeItemListStart
        \resumeItem{Managed \textbf{data migration} into CRM system, automating through UIPath \textbf{Robotic Process Automation}}
        \resumeItem{Contributed to website campaigns developing \textbf{front-end development} skills using HTML/CSS }
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{RapidReport} $|$ Accessibility Report Assistant $|$ \emph{Cohere, Google API, Next.js, TypeScript, Tailwind}}{DeltaHacks 2025}
          \resumeItemListStart
            \resumeItem{Developed \textbf{accessibility reporting web application} allowing users to document infrastructure issues through image uploads with AI-generated professional emails to businesses and government entities.}
            \resumeItem{Built frontend using \textbf{Next.js and Tailwind CSS} with screen reader compatibility and optimized color contrast for users with diverse accessibility needs.}
            \resumeItem{Utilized Google Geocode API to \textbf{automatically identify} and \textbf{route reports to nearest relevant recipients}.}
            \resumeItem{Integrated Cohere AI NLP to \textbf{generate professional emails} from uploaded images and text prompts.}
          \resumeItemListEnd
    \resumeProjectHeading
          {\textbf{Plant Pals} $|$ IoT Plant Monitor $|$ \emph{Arduino, HTML, CSS, JavaScript}}{Hack The North 2022}
          \resumeItemListStart
            \resumeItem{Collaborated to build \textbf{IoT plant monitoring system} integrating Arduino sensors with web dashboard.}
            \resumeItem{Resolved hardware compatibility issues through \textbf{adaptive problem-solving} developing my Arduino skills}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C, PostgreSQL, JavaScript, TypeScript, HTML/CSS} \\
     \textbf{Developer Tools}{: Git, VS Code, Cursor, GitHub, Visual Studio, PyCharm, JIRA, Jupyter Notebook} \\ 
     \textbf{Libraries}{: Pandas, NumPy, Matplotlib, Selenium, Dask, Beautiful Soup, Faker, Requests, Spring Framework, React}
    }}
 \end{itemize}

%-------------------------------------------

\end{document}
